---
title: "R practice"
output: html_document
editor_options: 
  chunk_output_type: console
---
Markdown allows you to do things like **bold**, _italic_, `code font`, and more!

Make a list with asterix like;
\*bold with double-asterix
\*Italicize with underscores
\*code-type font with backticks

for a numbered list:
1\. bold
1\. italic
1\. code

Hyperlinks are like [hyperlinked text](http://google.com)

```{r load data}
library(gapminder)
library(ggplot2)
gap <- gapminder
```

```{r make-plot}
plot(lifeExp~year, data= gap)
```

```{r}
temp <- c(1,2,3)
```

```{r make_cats}
cats <- data.frame(coat = c("calico","black","tabby"),
                   weight=c(2.1, 5.0, 3.2),
                   likes_string = c(1,0,1))
write.csv(x= cats, file = "data/feline-data.csv",
          row.names = FALSE)
```

```{r read_cats}
cats2 <- read.csv('data/feline-data.csv', stringsAsFactors = T)
```

cats$weight <- cats$weight +1

### Creating vectors and coercing types
```{r}
my_vector <- vector(mode='character',length=3)
combine_vector <- c(1,2,"bananas")
```

change names

```{r}
names(cats)[3] <- "likes_hunting"
```


Add columns and rows to a data frame
```{r}

cats <- read.csv('data/feline-data.csv')
age <- c(2,3,5)
cats <- cbind(cats,age)
newRow <- list("tortoiseshell",3.3,TRUE,9)
cats <- rbind(cats,newRow)
```

```{r}
human_age <- cats$age*7
human_age <- as.factor(human_age)
human_age <- as.numeric(as.character(human_age))/7
```

remove rows and columns

```{r}
cats$coat <- as.factor(cats$coat)
cats <- rbind(cats,c("white",3.4,0,1))
#remove a row
cats <- cats[-5,]
#cats <- na.omit(cats)
cats[,-4]

drop <- names(cats)%in% c('weight')
cats[,!drop]
```

```